Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-17 paper-2023-acsos-pulverization.tex
write something on the language choice

Also mention that is multiplatform

>>>>

We implemented the proposed \ac{acronym} in Kotlin.
%
We wanted a language with a strongly typed syntax to help developers with better contextual assist,
and we wanted the possibility to target multiple runtimes
(Kotlin currently targets the JVM, JavaScript, and native code for many platforms\footnote{\url{https://archive.is/JSiTg}},
including mobile and wearable devices)
and be as interoperable as possible with other languages.
%
Scala could have been a good alternative,
but we deemed the multiplatform support of Kotlin a better fit for our needs.
%
The framework has been open sourced and released with a permissive license\footnote{\url{https://github.com/nicolasfara/pulverization-framework}}.
